---
title       : Predicting Car Stopping Distance 
subtitle    : Developing Data Products Course Assignment
author      : Asier Goikoetxea
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

* We want to create a prediction model to determine the stopping distance of a car knowing the speed.
* We will use the "Cars" dataset from the "Datasets" package
* The Data has 50 observations and 2 variables: speed (mph) and dist (distance, ft)

```{r}
library(datasets)
data("cars")
summary(cars)
```

---  

## Fitting a Model

* For our prediction algorithm we will fit a basic linear model which relates Speed and Distance
* We can take a look a the coefficients to analyze the model
* in the next slide we will analyze some plots

```{r}
mdl <- lm(dist ~ speed, data = cars)
summary(mdl)$coef
```

---

## Model Analysis

```{r}
par(mfrow=c(2,2))
plot(mdl)
```

---

## Predicting new values

* We use the predict function to calculate new values using our linear model. For example, with a speed of 20 mph we would get these results

```{r}
userspeed <- 20; 
dist <- predict(mdl, newdata = data.frame(speed=userspeed))
print(dist)
```

---

## Ploting the Results

```{r}
plot(cars$speed, cars$dist, xlab="Car Speed (mph)", ylab = "Distance (ft)",
     col="blue") 
abline(mdl); lines(c(userspeed, userspeed), c(0, 200),col="red",lwd=3)
text(10, 120, paste("Distance = ", round(dist, digits = 3)))
```
